Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Overview.tex
fix

\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableSafeDeck2| defines a ``hierarchical overriding'' method. The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch. A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck2|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature. For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered. It does not really make sense to refine an old branch.

Similar to many OO languages, the model also allows \textit{super method invocation} in a method body. The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces. It should behave the same as \lstinline|new T().m()| in principle.

>>>>

\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableSafeDeck| defines a ``hierarchical overriding'' method. The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch. A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

A special rule for hierarchical overriding is: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature. For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered. It does not really make sense to refine an old branch.

% Similar to many OO languages, the model also allows \textit{super method invocation} in a method body. The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces. It should behave the same as \lstinline|new T().m()| in principle.
